Convex optimisation in communications with \texttt{cvxpy}

### 2017-08-08 article_cvxpy.tex
Rob changes, slight tweaks

\section{Example: power minimisation in communications}
\noindent For a real-world example consider a system of $n$ transmitters each of power $p_i$ and $m$ receivers, all in $2$D Euclidean space\cite{shannon1949}. The signal-to-interference-plus-noise ratio (SINR) is the strength of the desired signal $S$ relative to the interference power $I$ plus the background noise $\sigma$ at a receiver. How can we minimise the total power consumption $P$ of transmitters, yet achieve a minimum Signal to Interference plus Noise Ratio (SINR), $\gamma_0$, for all receivers? This question is relevant to telecoms companies who want to offer a service at a minimum quality standard. We formulate the problem with a given square path gain matrix $G$, background noise level $\sigma$ and a maximum power constraint $P_{\text{max}}$ of each transmitter:
\begin{align*}
&\underset{p}{\text{minimise}} \quad &&\sum_j p_j\\
&\text{subject to} \quad &&p_j \leq P_{\max}\\
& \quad &&p_j \geq 0\\
& \quad &&\gamma_i \geq \gamma_0.&&
\end{align*}

>>>>

\section{Example: power minimisation in communications}
\noindent To demonstrate the applicability \texttt{cvxpy} to  a real-world example, we consider a system of $n$ transmitters each of power $p_i$ and $m$ receivers, all in $2$D Euclidean space\cite{shannon1949}. In this problem we are constrained to having a minimum signal-to-interference-plus-noise ratio (SINR) at each receiver; the strength of the desired signal, $S$, relative to the interference power, $I$, plus the background noise, $\sigma$, at a receiver. How can we minimise the total power consumption, $P$, of transmitters, yet achieve this minimum SINR, $\gamma_0$, for all receivers? This question is relevant to telecoms companies who want to offer a service at a minimum quality standard. We formulate the problem with a given square path gain matrix, $G$, background noise level $\sigma$ and a maximum power constraint $P_{\text{max}}$ of each transmitter:
\begin{align*}
&\underset{p}{\text{minimise}} \quad &&\sum_j p_j\\
&\text{subject to} \quad &&p_j \leq P_{\max}\\
& \quad &&p_j \geq 0\\
& \quad &&\gamma_i \geq \gamma_0.&&
\end{align*}
